Matching Bullets

### 2015-12-07 imaging-paper.Rnw
Redescribe the caption
Smoothing factor paragraph

    p4
@
\end{subfigure}
%' \begin{subfigure}[t]{\linewidth}
%' \caption{\label{fig:loess_step5}Step 5 of the Loess fitting algorithm. The plot shows the result after trimming values below the first minimum, and above the second minimum.}
%' <<loess_step5, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE,  message=FALSE>>=
%' final.dat <- subset(curdata, y > curdata$y[min.left + 5] & y < curdata$y[min.right + (length(curdata$y) %/% 2) - 5])
%' 
%' qplot(data=final.dat, y, value) +
%'     theme_bw() + xlim(c(0,2500))
%' @
%' \end{subfigure}
\caption{Overview of all five steps of the loess algorithm to identify and remove big bullet strucure.}
\end{figure}

>>>>

    p4
@
\end{subfigure}
\caption{Overview of all seven steps of the smoothing algorithm to identify and remove grooves from the bullet images.}
\end{figure}

The ``smoothing factor" described in the algorithm represents the window size to use for a rolling average. Higher values of the smoothing factor therefore lead to more smoothed results. In the groove detection portion of this algorithm, we wish to remove most of the deviation but still maintain enough signal in the groove to detect it. Empirically, a value of 35 for the smoothing factor seems to work quite well. It is important to note that the smoothing pass is done twice. That is, the smoothed data is once again smoothed by computing a new rolling average with the same smoothing factor. This bears some similarities to the ideas of John Tukey in his book Exploratory Data Analysis, where he describes a smoothing process called ``twicing" in which a second pass is made on the residuals computed from the first pass [ref].
